\chapter{Features}
The tool supports

\section{Unsupported language features}
We provide a comprehensive list describing each language feature that is not 
supporte by the tool. Note that if the reader is reading this document in a pdf 
viewer, the names of the lists provide a link to sources for more information
about the missing part.

\subsection{Object-oriented paradigm}
No support for object-oriented concepts, except for the declaration of classes.
The following three concepts are the main ones that are not supported. Anything
that is built upon these conceps, e.g. calling a base class constructor, is also
not supported.

\begin{labeling}{abstract classes}
\item [\href{https://docs.oracle.com/javase/tutorial/java/concepts/inheritance.html}
            {inheritance}] Inheritance of a class or interface.
\item [\href{https://docs.oracle.com/javase/tutorial/java/concepts/interface.html}
            {interfaces}] An interface declaration.
\item [\href{https://docs.oracle.com/javase/tutorial/java/IandI/abstract.html}
            {abstract classes}] A class or method without an implementation.
\end{labeling} 

\subsection{Statements}
\begin{labeling}{synchronized statements}
\item [\href{https://docs.oracle.com/javase/tutorial/java/nutsandbolts/while.html}
            {do while loops}] \javainline{do \{ \} while(guard)}
\item [\href{https://docs.oracle.com/javase/tutorial/java/nutsandbolts/for.html}
            {for iterator loops}] \javainline{for (int item : numbers) \{ \}}
\item [\href{https://docs.oracle.com/javase/tutorial/essential/concurrency/locksync.html}
            {synchronized statements}] \javainline{synchronized(x) \{ \}}
\end{labeling}

\subsection{Expressions} 
\begin{labeling}{lambda expressions}
\item [\href{https://docs.oracle.com/javase/tutorial/java/javaOO/lambdaexpressions.html}
           {lambda expressions}] \javainline{(x) -> x*x}
\item [\href{https://docs.oracle.com/javase/tutorial/java/IandI/subclasses.html}
           {casting}] \javainline{(int)3.0}
\item [\href{https://docs.oracle.com/javase/tutorial/java/nutsandbolts/op2.html}
           {instance of}] \javainline{x instanceof Integer}
\item [\href{https://docs.oracle.com/javase/tutorial/java/javaOO/methodreferences.html}
           {method reference}] \javainline{Foo::bar}
\end{labeling}

\subsection{Others}
\begin{labeling}{static initialization blocks}
\item [\href{https://docs.oracle.com/javase/tutorial/java/javaOO/initial.html}
            {static initializer blocks}] Static block execution, which should be executed 
when the class is loaded.
\item [\href{https://docs.oracle.com/javase/tutorial/java/javaOO/initial.html}
            {static field initializer}] Static class field initialization, which should
be assigned when the class is loaded.
\item [\href{https://docs.oracle.com/javase/tutorial/java/javaOO/nested.html}
            {nested class definitions}] Class declarations inside classes or inside methods.
\item [\href{https://docs.oracle.com/javase/tutorial/java/generics/index.html}
            {generics}] Generic types, of any kind.
\item [\href{https://docs.oracle.com/javase/tutorial/java/javaOO/enum.html}
            {enums}] Enum declarations.
\end{labeling}